Extinction simulation on the metaweb

### 2022-09-20 random_network.Rmd
Add reanalysis with INLA

@@

# species
fish_species_tlvl <- node_tlvl %>%
  enframe(name = "node", value = "tlvl") %>%
  mutate(species = get_species(node)[, 1]) %>%
  filter(str_detect(species, "[A-Z]+")) %>%
  group_by(species) %>%
  summarise(tlvl_med = median(tlvl)) %>%
  arrange(desc(tlvl_med)) %>%
  deframe()
```

@@

  if (ncol(ff_metaweb) == 0) {
    ff_ind <- NA
    ct_ff <- NA
    tl_ff <- NA
    avg_tl_ff <- NA
    max_tl_ff <- NA
  } else {
    ff_ind <- NetIndices::GenInd(ff_metaweb)
    ct_ff <- ff_ind["C"]
    tl_ff <- NetIndices::TrophInd(ff_metaweb)$TL
    avg_tl_ff <- mean(tl_ff)
    max_tl_ff <- max(tl_ff)
  }

@@

  list(
    ff_metaweb = ff_metaweb,
    ind = ind,
    ff_ind = ff_ind,
    ct = ct,
    ct_ff = ct_ff,
    tl = tl,
    tl_ff = tl_ff,
    avg_tl = avg_tl,
    avg_tl_ff = avg_tl_ff,
    max_tl = max_tl,
    max_tl_ff = max_tl_ff
  )
}

@@

  if (ncol(ff_metaweb) == 0) {
    ff_ind <- NA
    ct_ff <- NA
    tl_ff <- NA
    avg_tl_ff <- NA
    max_tl_ff <- NA
  } else {
    ff_ind <- NA
    ct_ff <- sum(ff_metaweb) / (ncol(ff_metaweb) - 1)^2
    tl_ff <- NetIndices::TrophInd(ff_metaweb)$TL
    avg_tl_ff <- mean(tl_ff)
    max_tl_ff <- max(tl_ff)
  }

  if (ncol(x) == 0) {
    ind <- NA
    ct <- NA
    tl <- NA
    avg_tl <- NA
    max_tl <- NA
  } else {
    ind <- NA
    ct <- sum(x) / (ncol(x) - 1)^2
    tl <- NetIndices::TrophInd(x)$TL
    avg_tl <- mean(tl)
    max_tl <- max(tl)
  }

@@

  list(
    ff_metaweb = ff_metaweb,
    ind = ind,
    ff_ind = ff_ind,
    ct = ct,
    ct_ff = ct_ff,
    tl = tl,
    tl_ff = tl_ff,
    avg_tl = avg_tl,
    avg_tl_ff = avg_tl_ff,
    max_tl = max_tl,
    max_tl_ff = max_tl_ff
  )

@@

  node_extinction <- tibble(
    node_rm_single = names(ext_seq),
    node_tlvl = ext_seq,
    node_rm_tot = map(seq_along(ext_seq),
      ~ext_seq[1:.x]),
    metaweb = furrr::future_map(
      seq_along(ext_seq),
      ~metaweb[
        !rownames(net) %in% names(ext_seq)[1:.x],
        !colnames(net) %in% names(ext_seq)[1:.x]
        ]
    )
  )

@@

```{r, eval=FALSE}
plan(sequential)
sim_dec_tlvl <- get_sim_net(net = metaweb, ext_seq = node_fish_seq_dec_tlvl,
  keep_metaweb = FALSE)
sim_inc_tlvl <- get_sim_net(net = metaweb, ext_seq = node_fish_seq_inc_tlvl,
  keep_metaweb = FALSE
)
nsim <- 10

sim_random_tlvl <- tibble(
  repl = seq_len(nsim),
  sim = furrr::future_map(repl,
    ~get_sim_net(net = metaweb, ext_seq = sample(node_fish_seq_inc_tlvl),
      keep_metaweb = FALSE)
  )
)

@@

for (i in seq_along(fish_species_tlvl)) {
  decreasing_tlvl_metaweb <- metaweb[
    !str_detect(
      rownames(metaweb),
      paste0(names(fish_species_tlvl)[1:i], collapse = "|")
      ),
    !str_detect(
      colnames(metaweb),
      paste0(names(fish_species_tlvl)[1:i], collapse = "|")
      )
    ]
  sim_dec_tlvl_species[[i]] <- get_fw_metrics2(decreasing_tlvl_metaweb,
    keep_metaweb = FALSE)

  increasing_tlvl_metaweb <- metaweb[
    !str_detect(
      rownames(metaweb),
      paste0(names(inc_species_tlvl)[1:i], collapse = "|")
      ),
    !str_detect(
      colnames(metaweb),
      paste0(names(inc_species_tlvl)[1:i], collapse = "|")
      )
    ]
  sim_inc_tlvl_species[[i]] <- get_fw_metrics2(increasing_tlvl_metaweb,
    keep_metaweb = FALSE)
}
dec_species_result <- tibble(
  one_sp_rm = names(fish_species_tlvl),
  species_removed = map(seq_along(fish_species_tlvl),
    ~names(fish_species_tlvl)[1:.x]),
  metrics = sim_dec_tlvl_species
  )

@@

    tmp_metaweb <- metaweb[
      !str_detect(
        rownames(metaweb),
        paste0(sp_to_rm[[i]][[j]], collapse = "|")
        ),
      !str_detect(
        colnames(metaweb),
        paste0(sp_to_rm[[i]][[j]], collapse = "|")
      )
      ]
    sim_random_tlvl_species[[i]][[j]] <- get_fw_metrics2(
      tmp_metaweb,
    keep_metaweb = FALSE)
  }
}

>>>>

#

- Nombre de liens in and out

- Simulation avec degree in + out (somme des colonnes et des lignes)
- Rajouter extinction secondaire

@@

# species
fish_species_tlvl <- node_tlvl %>%
  enframe(name = "node", value = "tlvl") %>%
  mutate(species = get_species(node)[, 1]) %>%
  filter(str_detect(species, "[A-Z]+")) %>%
  group_by(species) %>%
  summarise(tlvl_med = median(tlvl)) %>%
  arrange(desc(tlvl_med)) %>%
  deframe()

@@

  if (ncol(ff_metaweb) == 0) {
    l_in_ff <- NA
    l_out_ff <- NA
    ff_ind <- NA
    ct_ff <- NA
    tl_ff <- NA
    avg_tl_ff <- NA
    max_tl_ff <- NA
  } else {
    l_in_ff <- colSums(ff_metaweb)
    l_out_ff <- rowSums(ff_metaweb)
    ff_ind <- NetIndices::GenInd(ff_metaweb)
    ct_ff <- ff_ind["C"]
    tl_ff <- NetIndices::TrophInd(ff_metaweb)$TL
    avg_tl_ff <- mean(tl_ff)
    max_tl_ff <- max(tl_ff)
  }

@@

  list(
    ff_metaweb = ff_metaweb,
    ind = ind,
    ff_ind = ff_ind,
    l_in_ff = l_in_ff,
    l_out_ff = l_out_ff,
    ct = ct,
    ct_ff = ct_ff,
    tl = tl,
    tl_ff = tl_ff,
    avg_tl = avg_tl,
    avg_tl_ff = avg_tl_ff,
    max_tl = max_tl,
    max_tl_ff = max_tl_ff
  )
}

@@

  if (ncol(ff_metaweb) == 0) {
    l_in_ff <- NA
    l_out_ff <- NA
    ff_ind <- NA
    ct_ff <- NA
    tl_ff <- NA
    avg_tl_ff <- NA
    max_tl_ff <- NA
  } else {
    l_in_ff <- colSums(ff_metaweb)
    l_out_ff <- rowSums(ff_metaweb)
    ff_ind <- NA
    ct_ff <- sum(ff_metaweb) / (ncol(ff_metaweb) - 1)^2
    tl_ff <- NetIndices::TrophInd(ff_metaweb)$TL
    avg_tl_ff <- mean(tl_ff)
    max_tl_ff <- max(tl_ff)
  }

  if (ncol(x) == 0) {
    l_in <- NA
    l_out <- NA
    ind <- NA
    ct <- NA
    tl <- NA
    avg_tl <- NA
    max_tl <- NA
  } else {
    l_in <- colSums(x)
    l_out <- rowSums(x)
    ind <- NA
    ct <- sum(x) / (ncol(x) - 1)^2
    tl <- NetIndices::TrophInd(x)$TL
    avg_tl <- mean(tl)
    max_tl <- max(tl)
  }

@@

  list(
    ff_metaweb = ff_metaweb,
    ind = ind,
    ff_ind = ff_ind,
    l_in = l_in,
    l_in_ff = l_in_ff,
    l_out = l_out,
    l_out_ff = l_out_ff,
    ct = ct,
    ct_ff = ct_ff,
    tl = tl,
    tl_ff = tl_ff,
    avg_tl = avg_tl,
    avg_tl_ff = avg_tl_ff,
    max_tl = max_tl,
    max_tl_ff = max_tl_ff
  )

@@

  node_extinction <- tibble(
    node_rm_single = names(ext_seq),
    node_tlvl = ext_seq,
    node_rm_tot = map(seq_along(ext_seq),
      ~ext_seq[1:.x]),
    metaweb = furrr::future_map(seq_along(ext_seq),
      function(x) {
      tmp <- metaweb[
        !rownames(net) %in% names(ext_seq)[1:x],
        !colnames(net) %in% names(ext_seq)[1:x]
        ]

      mask_link <- colSums(tmp) != 0
      return(tmp[mask_link, mask_link])
      }
    )
  )

@@

```{r, eval=FALSE}
library(furrr)
plan(sequential)
sim_dec_tlvl <- get_sim_net(net = metaweb, ext_seq = node_fish_seq_dec_tlvl,
  keep_metaweb = FALSE)
sim_inc_tlvl <- get_sim_net(net = metaweb, ext_seq = node_fish_seq_inc_tlvl,
  keep_metaweb = FALSE
)

nsim <- 10
sim_random_tlvl <- tibble(
  repl = seq_len(nsim),
  sim = furrr::future_map(repl,
    ~get_sim_net(net = metaweb, ext_seq = sample(node_fish_seq_inc_tlvl),
      keep_metaweb = FALSE)
  )
)

@@

for (i in seq_along(fish_species_tlvl)) {
  decreasing_tlvl_metaweb <- metaweb[
    !str_detect(
      rownames(metaweb),
      paste0(names(fish_species_tlvl)[1:i], collapse = "|")
      ),
    !str_detect(
      colnames(metaweb),
      paste0(names(fish_species_tlvl)[1:i], collapse = "|")
    )
    ]

  # Remove without feeding links
  mask_link <- colSums(decreasing_tlvl_metaweb) != 0
  decreasing_tlvl_metaweb <- tmp_metaweb[mask_link, mask_link]
  sim_dec_tlvl_species[[i]] <- get_fw_metrics2(decreasing_tlvl_metaweb,
    keep_metaweb = FALSE)

  increasing_tlvl_metaweb <- metaweb[
    !str_detect(
      rownames(metaweb),
      paste0(names(inc_species_tlvl)[1:i], collapse = "|")
      ),
    !str_detect(
      colnames(metaweb),
      paste0(names(inc_species_tlvl)[1:i], collapse = "|")
      )
    ]

  # Remove without feeding links
  mask_link <- colSums(increasing_tlvl_metaweb) != 0
  increasing_tlvl_metaweb <- tmp_metaweb[mask_link, mask_link]
  sim_inc_tlvl_species[[i]] <- get_fw_metrics2(increasing_tlvl_metaweb,
    keep_metaweb = FALSE)
}

dec_species_result <- tibble(
  one_sp_rm = names(fish_species_tlvl),
  species_removed = map(seq_along(fish_species_tlvl),
    ~names(fish_species_tlvl)[1:.x]),
  metrics = sim_dec_tlvl_species
  )

@@

    tmp_metaweb <- metaweb[
      !str_detect(
        rownames(metaweb),
        paste0(sp_to_rm[[i]][[j]], collapse = "|")
        ),
      !str_detect(
        colnames(metaweb),
        paste0(sp_to_rm[[i]][[j]], collapse = "|")
      )
      ]
    # Remove without feeding links
    mask_link <- colSums(tmp_metaweb) != 0
    tmp_metaweb <- tmp_metaweb[mask_link, mask_link]
    sim_random_tlvl_species[[i]][[j]] <- get_fw_metrics2(
      tmp_metaweb,
    keep_metaweb = FALSE)
  }
}
